PyBOP: A Python package for battery model optimisation and parameterisation

### 2024-12-04 joss/paper.preprint.tex
fixes: internal review feedback, minus figures

\affil[1]{Department of Engineering Science, University of Oxford,
Oxford, UK%
  }
\affil[2]{The Faraday Institution, Harwell Campus, Didcot, UK%
  }
\affil[3]{Research Software Engineering Group, University of Oxford,
Oxford, UK%
  }
\affil[4]{Quansight Labs%
  }
\affil[5]{Mathematics Institute, University of Warwick, Coventry, UK%
  }
\affil[$\mathparagraph$]{Corresponding author: %
   %
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\date{29 November 2024}

@@

The Python Battery Optimisation and Parameterisation (\texttt{PyBOP})
package provides a set of methods for the parameterisation and
optimisation of battery models, offering both Bayesian and frequentist
approaches with example workflows to assist the user. \texttt{PyBOP} has
been developed to enable parameter identification of various battery
models, including the electrochemical and equivalent circuit models
provided by the popular open-source \texttt{PyBaMM} package
(\citeproc{ref-Sulzer:2021}{Sulzer et al., 2021}).

Similarly, \texttt{PyBOP} can be used for parameter design optimisation
under user-defined operating conditions across a variety of model
structures. \texttt{PyBOP} allows battery model parameterisation using a
range of methods with diagnostics on the performance and convergence of
the identified or optimised parameters. The identified parameters can be
used for prediction, on-line control and design optimisation, all of
which support improved battery utilisation and development.

@@

\texttt{PyBOP} is a Python package designed to provide a user-friendly,
object-oriented interface for optimising battery models. \texttt{PyBOP}
leverages the open-source \texttt{PyBaMM} package
(\citeproc{ref-Sulzer:2021}{Sulzer et al., 2021}) to formulate and solve
of these battery models. \texttt{PyBOP} is intended to serve a broad
audience of students, engineers, and researchers in both academia and
the battery industry by enabling the use of predictive battery models
where previously this was not possible. \texttt{PyBOP} emphasises clear
and informative diagnostics and workflows for users of varying
expertise, by providing advanced optimisation and sampling algorithms.
These methods are provided through interfaces to \texttt{PINTS}
(\citeproc{ref-Clerx:2019}{Clerx et al., 2019}), \texttt{SciPy}
(\citeproc{ref-SciPy:2020}{Virtanen et al., 2020}), in addition to the
\texttt{PyBOP}'s own algorithms such as Adaptive Moment Estimation with
Weight Decay (AdamW), Gradient descent, and Cuckoo search.

\texttt{PyBOP} supports the Battery Parameter eXchange (BPX) standard
(\citeproc{ref-BPX:2023}{Korotkin et al., 2023}) for sharing battery
parameter sets. As these parameter sets are costly to obtain due to: the
equipment and time required for characterisation experiments, the need
for battery domain knowledge, and the computational cost of parameter
estimation. \texttt{PyBOP} reduces these costs by providing fast
computational estimation with parameter set interoperability.

This package complements other lithium-ion battery modelling packages
built around \texttt{PyBaMM}, such as \texttt{liionpack} for battery
pack simulation (\citeproc{ref-Tranter2022}{Tranter et al., 2022}) and
\texttt{pybamm-eis} for numerical impedance spectroscopy, as the
identified parameters from \texttt{PyBOP} are easily exportable.

@@

\texttt{PyBOP} has a layered data structure designed to compute and
process the forward model predictions and to package the necessary
information for the optimisation and sampling algorithms. The forward
model is solved using the popular battery modelling package,
\texttt{PyBaMM}, with construction, parameterisation, and discretisation
managed by \texttt{PyBOP}'s model interface to \texttt{PyBaMM}. This
approach provides a robust object construction process with a consistent
interface between the models and optimisers. The statistical methods and
optimisation algorithms are then constructed to interface cleanly with
the forward model predictions. Furthermore, identifiability metrics are
provided alongside the estimated parameters through Hessian
approximation of the cost functions in the frequentist workflows and
posterior moments in the Bayesian workflows.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{figures/PyBOP-high-level.pdf}
\caption{PyBOP's interface to supporting funding agencies, alongside a
visualisation of the general workflow for parameterisation and
optimisation \label{fig:high-level}}
\end{figure}

\texttt{PyBOP} formulates the inference process into four key classes,
namely the model, the problem, the cost, and the optimiser/sampler, as
shown in \autoref{fig:classes}. Each of these objects represents a base
class with child classes constructing specialised functionality for
inference or optimisation workflows. The model class constructs a
\texttt{PyBaMM} forward model for a given set of model equations
provided by \texttt{PyBaMM}, initial conditions, spatial discretisation,
and numerical solver. By composing \texttt{PyBaMM} directly into
\texttt{PyBOP}, specialised models can be constructed alongside the
standard models, which can be modified, and optimally constructed for
the inference tasks. One such example is spatial rediscretisation, which
is performed when geometric parameters are optimised. In this situation,
\texttt{PyBOP} minimally rediscretises the \texttt{PyBaMM} model while
maintaining the problem, cost, and optimiser objects, providing improved
performance benefits to users. Alongside construction of the forward
model, \texttt{PyBOP}'s model class provides methods for obtaining
sensitivities from the prediction, enabling gradient-based optimisation
algorithms. This prediction, along with it's corresponding
sensitivities, is provided to the problem class for processing and
exception control. A standardised data structure is then provided to the
cost classes, providing a distance, design, or likelihood-based metric
for optimisation. For deterministic optimisation, the optimisers
minimise the corresponding cost function or the negative log-likelihood
if a likelihood class is provided. Bayesian inference is provided by
Monte Carlo sampling classes, which accept the LogPosterior class and
sample from it using \texttt{PINTS} based Monte Carlo algorithms at the
time of submission. In the typical workflow, the classes in
\autoref{fig:classes} are constructed in sequence.

In addition to the core architecture, \texttt{PyBOP} provides several
specialised inference and optimisation processes. One such instance is
numerical electrochemical impedance spectroscopy predictions by
discretising the forward model into sparse mass matrix form with
accompanying auto-differentiated Jacobian. These objects are then
translated into the frequency domain with a linear solution used to
compute the battery model impedance. In this situation, the forward
models are constructed within the spatial rediscretisation workflow,
allowing for geometric parameter inference from EIS forward model
predictions. Furthermore, \texttt{PyBOP} builds on the \texttt{JAX}
(\citeproc{ref-jax:2018}{Bradbury et al., 2018}) numerical solvers
provided by \texttt{PyBaMM} by providing \texttt{JAX}-based cost
functions for automatic forward model differentiation with respect to
the parameters. This functionality provides a performance improvement
alongside an interface to JAX-based inference packages, such as
\texttt{Numpyro} (\citeproc{ref-numpyro:2019}{Phan et al., 2019}),
\texttt{BlackJAX} (\citeproc{ref-blackjax:2024}{Cabezas et al., 2024}),
and \texttt{Optax} (\citeproc{ref-optax:2020}{DeepMind et al., 2020}).

@@

As discussed above, \texttt{PyBOP} provides Bayesian inference methods
such as maximum a posteriori (MAP) alongside the point-based methods in
\autoref{tab:subclasses}; however, for a full Bayesian framework, Monte
Carlo sampling is implemented within \texttt{PyBOP}. These methods
construct a posterior distribution on the inference parameters, which
can be used for uncertainty and practical identifiability. The
individual sampler classes are currently composed within \texttt{PyBOP}
from the \texttt{PINTS} library, with a base sampling class implemented
for interoperability and direct integration with the \texttt{PyBOP}
model, problem, and likelihood classes. The currently supported samplers
are listed in \autoref{tab:samplers}.

@@

In general, battery models can be written in the form of a
differential-algebraic system of equations: \begin{equation}
\frac{\mathrm{d} \mathbf{x}}{\mathrm{d} t} = f(t,\mathbf{x},\mathbf{y},\mathbf{u}(t),\mathbf{\theta}),
\label{dynamics}
\end{equation} \begin{equation}
\mathbf{y}(t) = g(t,\mathbf{x},\mathbf{y},\mathbf{u}(t),\mathbf{\theta}),
\label{output}
\end{equation} with initial conditions \begin{equation}
\mathbf{x}(0) = \mathbf{x}_0(\mathbf{\theta}).
\label{initial_conditions}
\end{equation}

Here, \(t\) is time, \(\mathbf{x}(t)\) are the (spatially discretised)
states, \(\mathbf{y}(t)\) are the outputs (e.g.~the terminal voltage),
\(\mathbf{u}(t)\) are the inputs (e.g.~the applied current) and
\(\mathbf{\theta}\) are the unknown parameters.

Common battery models include various types of equivalent circuit models
(e.g.~the Thévenin model), the Doyle--Fuller--Newman (DFN) model
(\citeproc{ref-Doyle:1993}{Doyle et al., 1993};
\citeproc{ref-Fuller:1994}{Fuller et al., 1994}) based on porous
electrode theory and its reduced-order variants including the single
particle model (SPM) (\citeproc{ref-Planella:2022}{Planella et al.,
2022}), and the multi-species, multi-reaction (MSMR) model
(\citeproc{ref-Verbrugge:2017}{Verbrugge et al., 2017}). Simplified
models that retain acceptable predictive capabilities at a lower
computational cost are widely used, for example in battery management
systems, while physics-based models are required to understand the
impact of physical parameters on battery performance. This separation of
complexity traditionally results in multiple parameterisations for a
single battery type, depending on the model structure.

@@

The parameterisation of battery models is challenging due to the large
number of parameters that need to be identified compared to the
measurable outputs (\citeproc{ref-Andersson:2022}{Andersson et al.,
2022}; \citeproc{ref-Miguel:2021}{Miguel et al., 2021};
\citeproc{ref-Wang:2022}{Wang et al., 2022}). A complete
parameterisation often requires a stepwise identification of smaller
sets of parameters from a variety of different data sets
(\citeproc{ref-Chen:2020}{Chen et al., 2020};
\citeproc{ref-Chu:2019}{Chu et al., 2019}; \citeproc{ref-Kirk:2022}{Kirk
et al., 2023}) and excitations.

@@

where \(\mathcal{L} : \mathbf{\theta} \mapsto [0,\infty)\) is a cost (or
likelihood) function that quantifies the agreement between the model and
a sequence of observations \((\mathbf{y}_i)\) measured at times \(t_i\).
For gradient-based optimisers, the Jacobian of the cost function with
respect to the unknown parameters,
\((\frac{\partial \mathcal{L}}{\partial \theta})\) is computed for step
size and directional information.

Next, we demonstrate the fitting of synthetic data where the system
parameters are known. In this example problem, we use \texttt{PyBaMM}'s
implementation of the single particle model (SPM) with an added contact
resistance submodel. We assume that the battery model is already
parameterised except for two dynamic parameters, namely the lithium
diffusivity of the negative electrode active material particle (denoted
``negative particle diffusivity'') and the contact resistance. We
generate synthetic data from a one-hour discharge from 100\% state of
charge, to 0\% (denoted as 1C rate), followed by 30 minutes of
relaxation. This data is then corrupted with zero mean Gaussian noise of
amplitude 2mV, shown by the dots in
\autoref{fig:inference-time-landscape} (left). The initial states are
assumed known, although such an assumption is not generally necessary.
The underlying cost landscape explored by the optimiser is shown in
\autoref{fig:inference-time-landscape} (right).

@@

Moving forward, we will continue with identification in the time-domain.
As gradient information is available for this problem, the choice of
distance-based cost function and optimiser is not constrained. Due to
the different magnitudes of the two parameters, we apply the logarithmic
parameter transformation offered by \texttt{PyBOP}. This transforms the
optimisers search space of the optimiser to allow for a common step size
between the parameters, which is generally is not required, but improves
convergence in this problem. As a demonstration of the parameterisation
capabilities of \texttt{PyBOP}, \autoref{fig:convergence-min-max} (left)
shows the rate of convergence for each of the distance-minimising cost
functions, while \autoref{fig:convergence-min-max} (right) shows
analogous results for maximising a likelihood. The optimisation is
performed with SciPy Minimize using the gradient-based L-BFGS-B method.

@@

This parameterisation task can also be approached from a Bayesian
perspective, which we will present below using \texttt{PyBOP}'s sampler
methods. The optimisation equation presented in equation
\autoref{eqn:parameterisation} does not represent the Bayesian parameter
identification task, and as such we introduce the Bayes theorem as,

@@

@@

\bibitem[\citeproctext]{ref-Planella:2022}
Planella, F. B., Ai, W., Boyce, A. M., Ghosh, A., Korotkin, I., Sahu,
S., Sulzer, V., Timms, R., Tranter, T. G., Zyskin, M., Cooper, S. J.,
Edge, J. S., Foster, J. M., Marinescu, M., Wu, B., \& Richardson, G.
(2022). {A Continuum of Physics-Based Lithium-Ion Battery Models
Reviewed}. \emph{Progress in Energy}, \emph{4}(4), 042003.
\url{https://doi.org/10.1088/2516-1083/ac7d31}

>>>>

\affil[1]{Department of Engineering Science, University of Oxford,
Oxford, UK%
  }
\affil[2]{The Faraday Institution, Harwell Campus, Didcot, UK%
  }
\affil[3]{Research Software Engineering Group, University of Oxford,
Oxford, UK%
  }
\affil[4]{Quansight Labs%
  }
\affil[5]{Mathematics Institute, University of Warwick, Coventry, UK%
  }
\affil[$\mathparagraph$]{Corresponding author: %
   %
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\date{04 December 2024}

@@

The Python Battery Optimisation and Parameterisation (\texttt{PyBOP})
package provides methods for parameterising and optimising battery
models, offering both deterministic and stochastic approaches with
example workflows to assist users. \texttt{PyBOP} enables parameter
identification of various battery models, including the electrochemical
and equivalent circuit models provided by the popular open-source
\texttt{PyBaMM} package (\citeproc{ref-Sulzer:2021}{Sulzer et al.,
2021}).

Similarly, \texttt{PyBOP} can be used for design optimisation under
user-defined operating conditions across a variety of model structures
and design goals. \texttt{PyBOP} facilitates model parameterisation
using a range of methods, with diagnostics for examining the performance
and convergence of the resulting parameters. Identified parameters can
be used for prediction, on-line control, and design optimisation,
supporting improved battery utilisation and development.

@@

\texttt{PyBOP} is a Python package that provides a user-friendly,
object-oriented interface for optimising battery model parameters.
\texttt{PyBOP} leverages the open-source \texttt{PyBaMM} package
(\citeproc{ref-Sulzer:2021}{Sulzer et al., 2021}) to formulate and solve
battery models. \texttt{PyBOP} is intended to serve a broad audience
including students, engineers, and researchers in academia and industry,
enabling the use of battery models for performance prediction where
previously this was not possible without specialised knowledge of both
modelling, parameter inference and software development. \texttt{PyBOP}
emphasises clear and informative diagnostics and workflows to support
users with varying expertise, and provides access to a wide range of
different optimisation and sampling algorithms. These methods are
provided through interfaces to \texttt{PINTS}
(\citeproc{ref-Clerx:2019}{Clerx et al., 2019}), \texttt{SciPy}
(\citeproc{ref-SciPy:2020}{Virtanen et al., 2020}), and \texttt{PyBOP}'s
own algorithms such as adaptive moment estimation with weight decay
(AdamW), gradient descent, and Cuckoo search.

\texttt{PyBOP} supports the battery parameter exchange (BPX) standard
(\citeproc{ref-BPX:2023}{Korotkin et al., 2023}) for sharing battery
parameter sets. These parameter sets are typically costly to obtain due
to the specialised equipment and time required for characterisation
experiments, the need for battery domain knowledge, and the
computational cost of parameter estimation. \texttt{PyBOP} reduces these
costs by providing fast parameter estimation, standardised workflows,
and parameter set interoperability (via BPX).

This package complements other lithium-ion battery modelling packages
built around \texttt{PyBaMM}, such as \texttt{liionpack} for battery
pack simulation (\citeproc{ref-Tranter2022}{Tranter et al., 2022}) and
\texttt{pybamm-eis} for numerical impedance spectroscopy, since the
identified parameters from \texttt{PyBOP} are easily exportable to these
other packages.

@@

\texttt{PyBOP} has a layered structure designed to compute forward model
predictions, process the results, and package the necessary information
for the optimisation and sampling algorithms. The forward model is
solved using the popular battery modelling package, \texttt{PyBaMM},
with construction, parameterisation, and discretisation managed by
\texttt{PyBOP}'s model interface to \texttt{PyBaMM}. This provides a
robust object construction process with a consistent interface between
models and optimisers. The statistical methods and optimisation
algorithms are constructed to interface cleanly with the forward model
predictions. Furthermore, identifiability metrics are provided with the
estimated parameters (through Hessian approximation of the cost
functions in frequentist workflows, and posterior distributions in
Bayesian workflows).

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{figures/PyBOP-high-level.pdf}
\caption{PyBOP's interface to supporting funding agencies, alongside a
visualisation of the general workflow for parameterisation and
optimisation. \label{fig:high-level}}
\end{figure}

\texttt{PyBOP} formulates the inference process into four key classes,
namely the model, the problem, the cost, and the optimiser/sampler, as
shown in \autoref{fig:classes}. Each of these objects represents a base
class with child classes constructing specialised functionality for
inference or optimisation workflows. The model class constructs a
\texttt{PyBaMM} forward model for a given set of model equations
provided by \texttt{PyBaMM}, initial conditions, spatial discretisation,
and numerical solver. By composing \texttt{PyBaMM} directly into
\texttt{PyBOP}, specialised models can be constructed alongside the
standard models, which can be modified, and optimally constructed for
the inference tasks. One such example is spatial rediscretisation, which
is performed when geometric parameters are optimised. In this situation,
\texttt{PyBOP} minimally rediscretises the \texttt{PyBaMM} model while
maintaining the problem, cost, and optimiser objects, providing improved
performance benefits to users. Alongside construction of the forward
model, \texttt{PyBOP}'s model class provides methods for obtaining
sensitivities from the prediction, enabling gradient-based optimisation
algorithms. This prediction, along with its corresponding sensitivities,
is provided to the problem class for processing and exception control. A
standardised data structure is then provided to the cost classes, which
then computes a distance, design, or likelihood-based metric for
optimisation. For deterministic optimisation, the optimisers minimise
the corresponding cost function or the negative log-likelihood if a
likelihood class is provided. Bayesian inference is provided by Monte
Carlo sampling classes, which accept the LogPosterior class and sample
from it using \texttt{PINTS} based Monte Carlo algorithms at the time of
submission. In the typical workflow, the classes in
\autoref{fig:classes} are constructed in sequence.

In addition to the core architecture, \texttt{PyBOP} provides several
specialised inference and optimisation processes. One such instance is
parameter inference from EIS forward model predicitions. PyBOP
discretises the EIS forward model inso sparse mass matrix form with
accompanying auto-differentiated Jacobian. These objects are then
translated into the frequency domain with a linear solution used to
compute the battery model impedance. In this situation, the forward
models are constructed within the spatial rediscretisation workflow,
allowing for geometric parameter inference from EIS forward model
predictions. Furthermore, \texttt{PyBOP} builds on the \texttt{JAX}
(\citeproc{ref-jax:2018}{Bradbury et al., 2018}) numerical solvers
provided by \texttt{PyBaMM} by providing \texttt{JAX}-based cost
functions for automatic forward model differentiation with respect to
the parameters. This functionality provides a performance improvement,
and allows users to use many other JAX-based inference packages in order
to optimise their cost function, such as \texttt{Numpyro}
(\citeproc{ref-numpyro:2019}{Phan et al., 2019}), \texttt{BlackJAX}
(\citeproc{ref-blackjax:2024}{Cabezas et al., 2024}), and \texttt{Optax}
(\citeproc{ref-optax:2020}{DeepMind et al., 2020}).

@@

As discussed above, \texttt{PyBOP} provides both point-based
optimisation estimates \autoref{tab:subclasses} in addition to Monte
Carlo sampling routines in order to recover distributions of likely
parameter values. The Monte Carlco methods construct a posterior
distribution on the inference parameters, which can be used for
uncertainty and practical identifiability. The individual sampler
classes are currently composed within \texttt{PyBOP} from the
\texttt{PINTS} library, with a base sampling class implemented for
interoperability and direct integration with the \texttt{PyBOP} model,
problem, and likelihood classes. The currently supported samplers are
listed in \autoref{tab:samplers}.

@@

In general, battery models (after spatial discretisation) can be written
in the form of a differential-algebraic system of equations:
\begin{equation}
\frac{\mathrm{d} \mathbf{x}}{\mathrm{d} t} = f(t,\mathbf{x},\mathbf{\theta}),
\label{dynamics}
\end{equation} \begin{equation}
0 = g(t, \mathbf{x}, \mathbf{\theta})
\label{algebraic}
\end{equation} \begin{equation}
\mathbf{y}(t) = h(t,\mathbf{x}),
\label{output}
\end{equation} with initial conditions \begin{equation}
\mathbf{x}(0) = \mathbf{x}_0(\mathbf{\theta}).
\label{initial_conditions}
\end{equation}

Here, \(t\) is time, \(\mathbf{x}(t)\) are the (spatially discretised)
states, \(\mathbf{y}(t)\) are the outputs (e.g.~the terminal voltage)
and \(\mathbf{\theta}\) are the unknown parameters.

Common battery models include various types of equivalent circuit models
(e.g.~the Thévenin model), the Doyle--Fuller--Newman (DFN) model
(\citeproc{ref-Doyle:1993}{Doyle et al., 1993};
\citeproc{ref-Fuller:1994}{Fuller et al., 1994}) based on porous
electrode theory and its reduced-order variants including the single
particle model (SPM) (\citeproc{ref-Planella:2022}{Brosa Planella et
al., 2022}), and the multi-species, multi-reaction (MSMR) model
(\citeproc{ref-Verbrugge:2017}{Verbrugge et al., 2017}). Simplified
models that retain acceptable predictive capabilities at a lower
computational cost are widely used, for example in battery management
systems, while physics-based models are required to understand the
impact of physical parameters on battery performance. This separation of
complexity traditionally results in multiple parameterisations for a
single battery type, depending on the model structure.

@@

The parameterisation of battery models is challenging due to the large
number of parameters that need to be identified compared to the
measurable outputs (\citeproc{ref-Andersson:2022}{Andersson et al.,
2022}; \citeproc{ref-Miguel:2021}{Miguel et al., 2021};
\citeproc{ref-Wang:2022}{Wang et al., 2022}). A complete
parameterisation often requires a stepwise identification of smaller
sets of parameters from a variety of excitations and different data sets
(\citeproc{ref-Chen:2020}{Chen et al., 2020};
\citeproc{ref-Chu:2019}{Chu et al., 2019}; \citeproc{ref-Kirk:2022}{Kirk
et al., 2023}).

@@

where \(\mathcal{L} : \mathbf{\theta} \mapsto [0,\infty)\) is a cost
function that quantifies the agreement between the model,
\(\mathbf{y}(t_i)\) and a sequence of measured observations
\(\hat{\mathbf{y}_i}\) measured at times \(t_i\). Within the
\texttt{PyBOP} framework, the \texttt{FittingProblem} class packages the
model output along with the measured observations, both of which are
then passed to the \texttt{FittingCost} classes for the computation of
the specific cost function. For gradient-based optimisers, the Jacobian
of the cost function with respect to the unknown parameters,
\((\frac{\partial \mathcal{L}}{\partial \theta})\) is computed for step
size and directional information.

Next, we demonstrate the fitting of synthetic data where the system
parameters are known. In this example problem, we use \texttt{PyBaMM}'s
implementation of the single particle model (SPM) with an added contact
resistance submodel. We assume that the battery model is already
parameterised except for two dynamic parameters, namely the lithium
diffusivity of the negative electrode active material particle (denoted
``negative particle diffusivity'') and the contact resistance. We
generate synthetic data from a one-hour discharge from 100\% state of
charge, to 0\% (denoted as 1C rate), followed by 30 minutes of
relaxation. This data is then corrupted with zero mean Gaussian noise of
amplitude 2mV, shown by the dots in
\autoref{fig:inference-time-landscape} (left). The initial states are
assumed known, although such an assumption is not generally necessary.
The \texttt{PyBOP} repository contains multiple
\href{https://github.com/pybop-team/PyBOP/tree/develop/examples/notebooks}{example
notebooks} that follow a similar inference process for readers that
would like further information. The underlying cost landscape to be
explored by the optimiser is shown in
\autoref{fig:inference-time-landscape} (right) with the initial position
denoted alongside the known system parameters for this synthetic
inference task. In general, the true parameters are not known a priori.

@@

To avoid over complicating this example, we will continue with
identification in the time-domain; however, in general these two
forward-model prediction methods can be combined for improved system
excitation. As gradient information is available for this problem, the
choice of distance-based cost function and optimiser is not constrained.
Due to the different magnitudes of the two parameters, we apply the
logarithmic parameter transformation offered by \texttt{PyBOP}. This
transforms the optimisers search space of the optimiser to allow for a
common step size between the parameters, which is generally is not
required, but improves convergence in this problem. As a demonstration
of the parameterisation capabilities of \texttt{PyBOP},
\autoref{fig:convergence-min-max} (left) shows the rate of convergence
for each of the distance-minimising cost functions, while
\autoref{fig:convergence-min-max} (right) shows analogous results for
maximising a likelihood. The optimisation is performed with SciPy
Minimize using the gradient-based L-BFGS-B method.

@@

This parameterisation task can also be approached from a Bayesian
perspective, which we will present below using \texttt{PyBOP}'s sampler
methods. The optimisation equation presented in
\autoref{eqn:parameterisation} does not represent the Bayesian parameter
identification task, and as such we introduce the Bayes theorem as,

@@

\bibitem[\citeproctext]{ref-Planella:2022}
Brosa Planella, F., Ai, W., Boyce, A. M., Ghosh, A., Korotkin, I., Sahu,
S., Sulzer, V., Timms, R., Tranter, T. G., Zyskin, M., Cooper, S. J.,
Edge, J. S., Foster, J. M., Marinescu, M., Wu, B., \& Richardson, G.
(2022). {A Continuum of Physics-Based Lithium-Ion Battery Models
Reviewed}. \emph{Progress in Energy}, \emph{4}(4), 042003.
\url{https://doi.org/10.1088/2516-1083/ac7d31}

@@
